\TheTitle

### 2017-07-14 paper/introduction.tex
editing introduction

The DAG is able to provide a meaningful visualization in smaller
projects; it enables users to see when changes are made, when these
changes are merged, how each branch is interacting, and the point where
a branch forks from the master branch. In large modular projects, like
the Linux kernel, the DAG becomes a mess of merges and commits
(Figure~\ref{fig:gitk}) losing its visual meaning. In some cases, the
Linux kernel is simply too large for the system to generate a
visualization; Github provides a DAG view for many projects, but is
unable to display the visualization for projects at the scale of the
Linux of the kernel (Figure~\ref{fig:gitfail}). Between 60k and 70k new
commits are created for the Linux project every year; according to
previous work\cite{German2015}, a commit takes a median of 30 days from
the time it is authored until it arrives in the official repository. The
snapshot of the kernel tomorrow may be different than the snapshot from
today, containing new commits authored in the past; distinguishing these
new commits from the commits in the snapshot from today is not trivial.

One major challenge with visualizing the arrival of commits to a
repository is that Git does not store the date that a commit was merged
into another branch, including the master branch. To complicate the
problem, the DAG only has references to the ancestors of a commit (a
model necessary for the operation of Git), but maintainers would prefer
knowing the path a commit followed to reach the master repository.
Tracing a path that any commit followed to the master repository would
imply that for any given merge, it would be possible to know which
commits were merged. A user could inspect the commits that arrived into
the master branch within a given time-frame by checking which commits
were merged during that time-frame.

This paper makes three contributions; first, we describe a method of
converting the DAG of the Linux repository into the \mt of the
repository, that represents the path used by a commit to reach the
master branch; second, we present an implementation enabling the
inspection and visualization of merges in the Linux project using the
\mt modle; finally, we validate the \mt model and the implementation of
the visulization through a controlled user study. We further discuss the
issues of generalizing the model to other repositories, but present an
updated version that improves the performance of the algorithm by
pruning the DAG.\@

These methods and visualizations are implemented in a web-based tool
called \tool\footnote{\tool is currently available at
  \url{http://li.turingmachine.org}}. Our visualizations and tool
provide information about the location of any given commit or merge in
its respective merge-tree, the files edited, the modules edited, and the
commit message. \tool allows users to apply various filters, including
the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit hash. The user can
request all merges made by Linus that contain a commit or inner merge
that matches the search query, or just the commits and merges that match
the query.

>>>>

The DAG is able to provide a meaningful visualization in smaller
projects; it enables users to see when changes are made, when these
changes are merged, how each branch is interacting, and the point where
a branch forks from another branch. In large modular projects, like
the Linux kernel, the DAG becomes a mess of merges and commits
(Figure~\ref{fig:gitk}) losing its visual meaning. In some cases, the
Linux kernel is simply too large for the system to generate a
visualization; Github provides a DAG view for a repository, but is
unable to display the visualization for projects at the scale of the
Linux of the kernel (Figure~\ref{fig:gitfail}). Between 60k and 70k new
commits are created for the Linux project every year; according to
previous work\cite{German2015}, a commit takes a median of 30 days from
the time it is authored until it arrives in the official repository. The
snapshot of the kernel tomorrow may be different than the snapshot from
today, containing new commits authored in the past; distinguishing these
new commits from the commits in the snapshot from today is not trivial.

One major challenge with visualizing the arrival of commits to a
repository is that Git does not store the date that a commit was merged
into another branch, including the master branch. To complicate the
problem, the DAG only has references to the parents of a commit (a
model necessary for the operation of Git), but maintainers would prefer
knowing the path a commit followed to reach the master repository.
Tracing a path that any commit followed to the master repository would
imply that for any given commit, we know the next merge in the direction
of the master branch. A user could inspect the commits that arrived into
the master branch within a given time-frame by checking which commits
were merged during that time-frame.

This paper makes three contributions; first, we describe a method of
converting the DAG of the Linux repository into the \mt of the
repository, that represents the path used by a commit to reach the
master branch; second, we present an implementation enabling the
inspection and visualization of merges in the Linux project using the
\mt model; third, we validate the \mt model and the implementation of
the visualization through a controlled user study. We further discuss the
issues of generalizing the model to other repositories, but present an
updated version that improves the performance of the algorithm by
pruning the DAG.\@

These methods and visualizations are implemented in a web-based tool
called \tool\footnote{\tool is currently available at
  \url{http://li.turingmachine.org}}. Our visualizations and tool
provide information about the location of any given commit or merge in
its respective merge-tree, the files edited, the modules edited, and the
commit message. \tool provides a search engine that filters commits by
commit hash, terms from the commit log, the author, filenames, and other
information. The results are then grouped together by the root of the
corresponding \mt.
